\documentclass[letterpaper,10pt,draftclsnofoot,onecolumn,titlepage]{IEEEtran}

\usepackage{graphicx}                                        
\usepackage{amssymb}                                         
\usepackage{amsmath}                                         
\usepackage{amsthm}                                          

\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage{url}

\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}

\usepackage{geometry}

\geometry{margin = .75in}
\geometry{textheight=8.5in, textwidth=6in}

%random comment

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\newcommand{\toc}{\tableofcontents}

%\usepackage{hyperref}

\def\name{Courtney Bonn, Isaac Chan}
\def\grp{Group \#39}

%pull in the necessary preamble matter for pygments output
%\input{pygments.tex}

%% The following metadata will show up in the PDF properties
% \hypersetup{
%   colorlinks = false,
%   urlcolor = black,
%   pdfauthor = {\name},
%   pdfkeywords = {cs311 ``operating systems'' files filesystem I/O},
%   pdftitle = {CS 311 Project 1: UNIX File I/O},
%   pdfsubject = {CS 311 Project 1},
%   pdfpagemode = UseNone
% }

\parindent = 0.0 in
\parskip = 0.1 in

\begin{document}

\title{Project 1: Getting Acquainted}
\author{\name \\ \grp}

\maketitle

\begin{abstract}
Abstract here.
\end{abstract}

\clearpage

%input the pygmentized output of mt19937ar.c, using a (hopefully) unique name
%this file only exists at compile time. Feel free to change that.
Seeing if changes are being pulled correctly. 

\begin{itemize}
	\item A log of commands used to perform the requested actions, as well as a write-up of your concurrency solution.
	\item An explanation of each and every flag in the listed qemu command-line
	\item Answer the following questions in sufficient detail (for the concurrency):
    \begin{enumerate}  
		\item What do you think the main point of this assignment is?
		\item How did you personally approach the problem? Design decisions, algorithm, etc.
		\item How did you ensure your solution was correct? Testing details, for instance.
		\item What did you learn?
 	\end{enumerate}
	\item Version control log (formatted as a table) -- there are any number of tools for generating a TeX table from repo logs
	\item Work log. What was done when? Be detailed.
\end{itemize}

%\section*{Appendix 1: Source Code}
%\input{__mt19937ar.c.tex}

\end{document}
