\documentclass[letterpaper,10pt,draftclsnofoot,onecolumn,titlepage]{IEEEtran}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{alltt}
\usepackage{float}
\usepackage{color}
\usepackage{url}
\usepackage{enumitem}
%\usepackage{pstricks, pst-node}
\usepackage{geometry}
\usepackage{bookmark}

\geometry{margin = .75in}

\usepackage{hyperref}


\def\name{Courtney Bonn, Isaac Chan}
\def\grp{Group \#39}

\hypersetup{
	colorlinks = true,
	urlcolor = black,
	pdfauthor = {\name},
	pdftitle = {CS 444, Project 2},
	pdfsubject = {CS 444, Project 2},
	pdfpagemode = UseNone
}

\begin{document}

\title{Project 2: I/O Elevators}
\author{\name \\ \grp}

\maketitle

\begin{abstract}
For the second kernel assignment, we are tasked with building a new I/O Scheduler that is based off of the current NOOP Scheduler in the Linux Kernel. 
The algorithm that will be used for the new I/O Scheduler is CLOOK. 
\end{abstract}

\clearpage
\section{Design Plan}
The algorithm we chose to implement is CLOOK. After examining the NOOP scheduler, we came to the conclusion that the only two methods to be altered 
are the dispatch and add\_request methods. The dispatch requires an addition to tell if the request is for reading or writing. The add\_request method 
requires an addition to put a new request into the queue. Because the CLOOK algorithm is circular, the request must be put in the correct spot in the 
queue. This can be done by: check the sector position while iterating and then insert the request if the sector is larger. 
    
\section{Version Control Log}
%\input{changelog.tex}

\section{Work Log}
\begin{center}
\begin{tabular}{p{3cm}p{1cm}p{1cm}p{10cm} }
 Date  & Time & Person & Event \\ \hline
October 25, 2017 & 5:15pm & Courtney & Began Project 2 LaTeX file \\
		 & 6:15pm & Courtney & Changes Tex Template to match Project 2 and made sure it compiled correctly with "make" \\
October 29, 2017 & 11:30am & Courtney & Started reading Chapter 14 of Love's Kernel book \\                 
		 & 11:45am & Courtney & Copied noop-iosched.c to our working directory, renamed it sstf-iosched.c, and changed instances of noop to look \\ 
		 & 12:00pm & Courtney & Continued research on NOOP, LOOK, and C-LOOK algorithms \\
		 & 10:00pm & Courtney & Working on getting the VM run with the NOOP Scheduler \\
   		 & 10:30pm & Isaac & Examine NOOP scheduler and understand how it works \\
   		 & 11:30pm & Isaac & Design a plan to implement CLOOK algorithm \\
   		 & 11:45pm & Isaac & Begin implementation of CLOOK algorithm \\
October 30, 2017 & 12:30am & Isaac & Complete initial CLOOK implementation \\
		 & 1:00am & Courtney & Working on Kernel error \\
		 & 1:51am & Isaac & Recopied Yocto directory with changed files to rebuild the kernel \\
		 & 1:55am & Isaac & Successfully built the kernel with the new scheduler \\
		 & 2:05am & Courtney & Ran qemu with new scheduler and confirmed that clook scheduler is the default in the VM \\
   		 & 2:20am & Courtney & Design a plan to test the new scheduler \\
		 & 3:45am & Courtney & Still working on how to test scheduler \\
		 & 4:47am & Courtney and Isaac & Trying to figure out why CLOOK scheduler isn't printing/working, not having much success \\
		 & 5:30pm & Courtney and Isaac & Working through Kernel Panic, trying to determine where the error is \\ 
\end{tabular}
\end{center}

\section{Write Up}
\begin{enumerate}
                \item What do you think the main point of this assignment is? \\
The main point of this assignment is to learn how to work with the disk scheduler, or I/O scheduler, on the kernel. 
Using the current I/O schedulers as base algorithms to work off of, we will build a CLOOK algorithm on the NOOP scheduler. 
                \item How did you personally approach the problem? Design decisions, algorithm, etc. \\
This assignment took a lot of research ahead of time before actually sitting down to work on the code. 
First off, we needed to understand what the current algorithm was doing. 
NOOP is essentially a first-come-first-served (FCFS) or FIFO algorithm, meaning whatever request it receives first is the first one it is going to process. 
Additionally, it does not do any sorting. It does sort a new request with adjacent requests. 

CLOOK is a circular variant of LOOK. It only scans in one direction and starts at the beginning when it reaches the end. When a new request arrives it must 
be sorted to the correct spot in the queue.

To implement our selected algorithm, we made use of the Kernel's Linked List implementation. 
                \item How did you ensure your solution was correct? Testing details, for instance.

Our plan for testing was to run a python script that created a file and wrote to it. 
                \item What did you learn?
                \item How should the TA evaluate your work? Provide detailed steps to prove correctness 
\end{enumerate}



\end{document}
